Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-10-03 ms/ms.Rmd
ms: add predictors table

We created the same suite of 25 quantitative peat depth predictors for both sites.
All predictors were derived either from an airborne radiometric survey or from a digital terrain model.
From the radiometric surveys we simply used the four variables produced by the surveyors (Geological Survey of Norway): ground concentration of Potassium, Thorium, Uranium, as well as total count.
From the digital terrain models we calculated several simple terrain variables and a series of more complex geomorphometric and hydrological variables.

>>>>

We created the same suite of 25 quantitative peat depth predictors for both sites (Table \@ref(tab:preds)).
All predictors were derived either from an airborne radiometric survey or from a digital terrain model.
From the radiometric surveys we simply used the four variables produced by the surveyors (Geological Survey of Norway): ground concentration of Potassium, Thorium, Uranium, as well as total count.
From the digital terrain models we calculated several simple terrain variables and a series of more complex geomorphometric and hydrological variables.

```{r preds, echo=FALSE, message=FALSE}
df <- readr::read_csv("tables/predictors.csv")
knitr::kable(df, booktabs = FALSE, caption = "Quantitative predictors of peat depth.")
```

### 2024-10-03 ms/ms.tex
ms: add predictors table

We created the same suite of 25 quantitative peat depth predictors for both sites.
All predictors were derived either from an airborne radiometric survey or from a digital terrain model.
From the radiometric surveys we simply used the four variables produced by the surveyors (Geological Survey of Norway): ground concentration of Potassium, Thorium, Uranium, as well as total count.
From the digital terrain models we calculated several simple terrain variables and a series of more complex geomorphometric and hydrological variables.

>>>>

We created the same suite of 25 quantitative peat depth predictors for both sites (Table \ref{tab:preds}).
All predictors were derived either from an airborne radiometric survey or from a digital terrain model.
From the radiometric surveys we simply used the four variables produced by the surveyors (Geological Survey of Norway): ground concentration of Potassium, Thorium, Uranium, as well as total count.
From the digital terrain models we calculated several simple terrain variables and a series of more complex geomorphometric and hydrological variables.

\caption{\label{tab:preds}Quantitative predictors of peat depth.}
\centering
\begin{tabular}[t]{l|l}
\hline
name & description\\
\hline
radK & Potassium ground concentration\\
\hline
radTh & Thorium ground concentration\\
\hline
radU & Uranium ground concentration\\
\hline
radTC & Total count of gamma radiation\\
\hline
elevation & Mean elevation\\
\hline
slope1m & Mean of 1 m slope\\
\hline
TPI1m & Mean of 1 m topographic position index\\
\hline
TRI1m & Mean of 1 m terrain ruggedness index\\
\hline
roughness1m & Mean of 1 m roughness\\
\hline
slope10m & 10 m slope\\
\hline
TPI10m & 10 m topographic position index\\
\hline
TRI10m & 10 m terrain ruggedness index\\
\hline
roughness10m & 10 m roughness\\
\hline
MRVBF & Multi-resolution valley bottom flatness\\
\hline
TWI5m & Mean of 5 m topographic wetness index\\
\hline
TWI10m & 10 m topographic wetness index\\
\hline
TWI20m & Bilinear interpolation of 20 m topographic wetness index\\
\hline
TWI50m & Bilinear interpolation of 50 m topographic wetness index\\
\hline
DTW2500 & Depth-to-water index, flow initiation area of 2500 m\textasciicircum{}2\\
\hline
DTW5000 & Depth-to-water index, flow initiation area of 5000 m\textasciicircum{}2\\
\hline
DTW10000 & Depth-to-water index, flow initiation area of 10000 m\textasciicircum{}2\\
\hline
DTW20000 & Depth-to-water index, flow initiation area of 20000 m\textasciicircum{}2\\
\hline
DTW40000 & Depth-to-water index, flow initiation area of 40000 m\textasciicircum{}2\\
\hline
DTW80000 & Depth-to-water index, flow initiation area of 80000 m\textasciicircum{}2\\
\hline
DTW160000 & Depth-to-water index, flow initiation area of 160000 m\textasciicircum{}2\\
\hline
\end{tabular}
\end{table}
